Robust Spectroscopic Inference with Imperfect Models

### 2014-09-22 tex/paper.tex
PCA work begun

\acknowledgments  List your acknowledgments (don't forget anyone!).  I can think of: 
Foreman-Mackey, Hogg, people on Johnson's group?, Lars?, TRES archive people?  You might want to 
acknowledge your NSF Fellowship here, and the Smithsonian Institution (how you're being paid now), 
for funding.  Figures \ref{fig:Kurucz_posterior}, \ref{fig:PHOENIX_posterior}, and \ref{fig:Gl51_posterior} were generated with \texttt{triangle.py} \citep{foreman-mackey14}. \\

@@

\begin{figure}[!b]
\begin{center}
  \includegraphics{figs/interp_matrix.pdf}
  \figcaption{A sub-region of a typical interpolation error kernel, $\mathcal{K}_{\ij}^{\rm int}$, 
for an arbitrary set of parameters; $\vt_{\ast} = T_\textrm{eff} = 6220$, K, $\log g=4.2$ dex, and 
$\Z = $-0.4 dex$]$.  The color scale is the same as in Fig.~\ref{fig:matrix}; since elements of 
this covariance kernel can be negative, an analogous scale (in {\it red}) is duplicated to 
highlight such regions with the same logarithmic stretch.  \label{fig:interp_matrix}}
\end{center}
\end{figure}

>>>>

\acknowledgments  The authors would like to graciously acknowledge the following people for many helpful discussions and key insights: Gregory M. Green, Kaisey Mandel, Daniel Foreman-Mackey, John Johnson and the ExoLab, Daniel Eisenstein, Allyson Bieryla, and Maxwell Moe.  IC was supported by the NSF Graduate Fellowship and the Smithsonian Institution. Figures \ref{fig:Kurucz_posterior}, \ref{fig:PHOENIX_posterior}, and \ref{fig:Gl51_posterior} were generated with \texttt{triangle.py} \citep{foreman-mackey14}. Astropy. JuliaLang.\\

@@

\begin{figure}[!b]
\begin{center}
  \includegraphics{figs/interp_matrix.pdf}
  \figcaption{A sub-region of a typical interpolation error kernel, $\mathcal{K}_{\ij}^{\rm int}$, 
for an arbitrary set of parameters; $\vt_{\ast} = T_\textrm{eff} = 6220$, K, $\log g=4.2$ dex, and 
$\Z = $-0.4 dex.  The color scale is the same as in Fig.~\ref{fig:matrix}; since elements of 
this covariance kernel can be negative, an analogous scale (in {\it red}) is duplicated to 
highlight such regions with the same logarithmic stretch.  \label{fig:interp_matrix}}
\end{center}
\end{figure}
